Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2024-08-25 Thesis/01-chap1.qmd
fill in last part

The lineup protocol has gained increasing traction in recent years and has already been integrated into data analysis of various topics [see @loy2013diagnostic; @widen2016graphical; @krishnan2021hierarchical]. However, the reliance of human assessment is a fundamental aspect of visual tests, which may restrict its widespread usage. The lineup protocol is unsuitable for large-scale applications, due to its high labour costs and time requirements. Moreover, it presents significant usability issues for individuals with visual impairments, resulting in reduced accessibility.

>>>>

The lineup protocol has gained increasing traction in recent years and has already been integrated into data analysis of various topics [see @krishnan2021hierarchical; @loy2013diagnostic; @widen2016graphical]. However, the reliance of human assessment is a fundamental aspect of visual tests, which may restrict its widespread usage. The lineup protocol is unsuitable for large-scale applications, due to its high labour costs and time requirements. Moreover, it presents significant usability issues for individuals with visual impairments, resulting in reduced accessibility.
